The Near and Mid-infrared photometric properties of known redshift $z\geq5$ Quasars

### 2020-01-10 tex/MNRAS_submission/rv1/referees_reply.txt

	We thank the Referee for reading our manuscript carefully and
	for their review and comments.  We address each and every one
	of these in turn below (indented text).

	We have also made further, key improvements to our dataset and
	pipeline.

	We note that after the submission of the original manuscript
	it was brought to our attention (K. Perger; priv. comm) that
	we were missing 25 confirmed z>5 quasars.  As such, our
	database has increased by 25 objects for a total of 488 VHzQs.

	As such all six Tables have been updated accordingly, as have
	Figures 2 and 3.

@@

p. 2, Fig. 1: Is it useful here to plot both filter sets if they are sufficiently
different? Please provide larger tick-marks for better readability in any case.

	   We have enbiggened the  tick-marks.

	   The ZYJHK filters for UKIRT and VISTA *are* different, but
	   plotting both doesn't result in a clear figure.

	   ....
		I think adding an explicit link to:
	          d80b2t/VHzQ/SEDs/filters_vs_QSOstars_UKIRT.png
	  and
	         d80b2t/VHzQ/SEDs/filters_vs_QSOstars_VISTA.png
	 is the way forward here.

p. 3, Fig. 2, caption or text: You should briefly comment on why the quasar
distribution has this gap in N(z) at z~5.5?. Is this because of the relativity
sensitivity across the filter curves, and/or the onset of complete GP-troughs at
z>5.7?

	And I think this is where some of the missing objects come in??
	We’ll need to update: Tables 1, 2 and obviously 3 once we have those extra objects.

@@

    	Checked and updated.

p. 5: [My only (minor) scientific comment]: Re: ``although possible, we consider
it highly unlikely there would be more than one MIR source contributing to the
flux of a single UV/optically bright rest-frame quasar. Investigating this in
detail is very interesting but left to a future study. ''

I think it would be better to address now the number of expected contaminating
8--25 micron sources in the apertures used, as it can be done straightforwardly.
E.g., Driver et al. (2016, ApJ, 827, 107; astro-ph/1605.01523) --- the figures
you need for this estimate are actually best given as Fig. A4, A5 on the astro-ph
version. The redshift distribution of the sampled 8--25 micron foreground objects
is narrow enough and their K-corrections advantageous enough, that the objects
counts sharply turnover for AB(W3, W4) > 20--18 mag (left panels), and as a
consequence the normalized differential counts (right panels) --- especially in
W4 --- have most of their EBL energy emerging at AB~18--20 mag. As a consequence,
the relative number or probability of contaminating objects at AB>20 mag inside
your apertures should be rather small. A point worth mentioning, as it helps your
case.

		NPR has added approriated words in the text to address
		this good point.

### 2020-01-10 tex/MNRAS_submission/rv1/referees_reply.txt

	   The ZYJHK filters for UKIRT and VISTA *are* different, but
	   plotting both doesn't result in a clear figure.

	   ....
		I think adding an explicit link to:
	          d80b2t/VHzQ/SEDs/filters_vs_QSOstars_UKIRT.png
	  and
	         d80b2t/VHzQ/SEDs/filters_vs_QSOstars_VISTA.png
	 is the way forward here.

p. 3, Fig. 2, caption or text: You should briefly comment on why the quasar
distribution has this gap in N(z) at z~5.5?. Is this because of the relativity
sensitivity across the filter curves, and/or the onset of complete GP-troughs at
z>5.7?

	[And I think this is where some of the missing objects come in??
	We’ll need to update: Tables 1, 2 and obviously 3 once we have those extra objects.]

@@

    	Checked and updated.

p. 5: [My only (minor) scientific comment]: Re: ``although possible, we consider
it highly unlikely there would be more than one MIR source contributing to the
flux of a single UV/optically bright rest-frame quasar. Investigating this in
detail is very interesting but left to a future study. ''

I think it would be better to address now the number of expected contaminating
8--25 micron sources in the apertures used, as it can be done straightforwardly.
E.g., Driver et al. (2016, ApJ, 827, 107; astro-ph/1605.01523) --- the figures
you need for this estimate are actually best given as Fig. A4, A5 on the astro-ph
version. The redshift distribution of the sampled 8--25 micron foreground objects
is narrow enough and their K-corrections advantageous enough, that the objects
counts sharply turnover for AB(W3, W4) > 20--18 mag (left panels), and as a
consequence the normalized differential counts (right panels) --- especially in
W4 --- have most of their EBL energy emerging at AB~18--20 mag. As a consequence,
the relative number or probability of contaminating objects at AB>20 mag inside
your apertures should be rather small. A point worth mentioning, as it helps your
case.

		We have added approriated words in the text to address this good point.

### 2020-01-10 tex/MNRAS_submission/rv1/VHzQ_MNRAS_rv1.tex
referees_reply.txt updated

Previous works \citep[e.g., ][]{Krawczyk2013, Ross2015, Bilicki2016} found that cross-matches performed with a radius of 2-3'' between the user catalogue and WISE was a good compromise between completeness and contamination \citep[see e.g. Figure 4 of ][]{Krawczyk2013}. We thus use a cross-match radius of 2.75''. When querying the AllWISE catalogues, ``Cone Search Radius'' in the AllWISE table search was set to 2.75'' for the Spatial Constraints. The ``One to One Match'' was ``not'' checked; although possible, we consider it highly unlikely there would be more than one MIR source contributing to the flux of a single UV/optically bright rest-frame quasar. Investigating this in detail is very interesting but left to a future study.

@@

Quasars are known to have dramatically changing Balmer lines,
especially H$\beta$ \citep[e.g.,][]{LaMassa2015, Ruan2016, Runnoe2016,
Macleod2016, Gezari2017, Runco2016, YangQ2018, Assef2018, Stern2018,
Ross2018, MacLeod2019, Graham2019}. As a guide, we note that H$\alpha$
is redshifted to 3.94$\mu$m (i.e. W1) at $z=5.00$ and 5.57$\mu$m,
which is between the W2 and W3-bands at $z=7.50$.  H$\beta$ is
redshifted to 2.92$\mu$m, which is the blue edge of W1, at $z=5.00$
and 4.13$\mu$m at $z=7.50$. Less well understood is the temporal
behaviour of the metal lines, in particular \civ and \mgii.  \civ
enters the $Y$-band at redshift $z$=5.32 and exits at $z$=5.99, and
enters the $J$-band at redshift $z=6.55$ and exits at $z$=7.57. \mgii
enters the $H$-band at redshift $z=4.33$ and exits at $z=5.37$ and
enters the $K$-band at redshift $z=6.25$ and exits at $7.50$.

>>>>

Previous works \citep[e.g., ][]{Krawczyk2013, Ross2015, Bilicki2016} found that cross-matches performed with a radius of 2-3'' between the user catalogue and WISE was a good compromise between completeness and contamination \citep[see e.g. Figure 4 of ][]{Krawczyk2013}. We thus use a cross-match radius of 2.75''. When querying the AllWISE catalogues, ``Cone Search Radius'' in the AllWISE table search was set to 2.75'' for the Spatial Constraints. The ``One to One Match'' was ``not'' checked; although possible, we consider it highly unlikely there would be more than one MIR source contributing to the flux of a single UV/optically bright rest-frame quasar. As a check, we utilize data from the {\it Spitzer} Space Telescope in IRAC Channel 2 4.5$\mu$m,  IRAC Channel 4 8$\mu$m and MIPS 24$\mu$m,  and number counts and luminosity density measurements from \citet[][see their Figures 8.11, 8.12 and 8.13]{Driver2016}. 
%% address now the number of expected contaminating 8--25 micron sources in the apertures used, as it can be done straightforwardly. E.g., Driver et al. (2016, ApJ, 827, 107; astro-ph/1605.01523) --- the figures you need for this estimate are actually best given as Fig. A4, A5 on the astro-ph version.
The redshift distribution of the sampled 8--24 $\mu$m foreground objects is narrow enough and their $K$-corrections advantageous enough, that the objects
counts sharply turnover for $AB(W3, W4) \gtrsim 20$mag, and the normalized differential counts --- especially in e.g. WISE W4 --- have most of their  extragalactic background light energy emerging at AB$\sim$18--20 mag. As a consequence, the relative number or probability of contaminating objects at AB$>20$mag inside our apertures should be small.  %Investigating this in detail is very interesting but left to a future study.

@@

Quasars are known to have dramatically changing Balmer lines,
especially H$\beta$ \citep[e.g.,][]{LaMassa2015, Ruan2016, Runnoe2016,
Macleod2016, Gezari2017, Runco2016, YangQ2018, Assef2018, Stern2018,
Ross2018, MacLeod2019, Graham2019b}. As a guide, we note that H$\alpha$
is redshifted to 3.94$\mu$m (i.e. W1) at $z=5.00$ and 5.57$\mu$m,
which is between the W2 and W3-bands at $z=7.50$.  H$\beta$ is
redshifted to 2.92$\mu$m, which is the blue edge of W1, at $z=5.00$
and 4.13$\mu$m at $z=7.50$. Less well understood is the temporal
behaviour of the metal lines, in particular \civ and \mgii.  \civ
enters the $Y$-band at redshift $z$=5.32 and exits at $z$=5.99, and
enters the $J$-band at redshift $z=6.55$ and exits at $z$=7.57. \mgii
enters the $H$-band at redshift $z=4.33$ and exits at $z=5.37$ and
enters the $K$-band at redshift $z=6.25$ and exits at $7.50$.
